%-------------------------
% Resume in Latex
% Author : Sergio Rivera
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\newcommand{\bcomment}[1]{}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
% Items
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Role headers
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Role sub-headers
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Project headers
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% Bullets
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Item lists
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%==========RESUME CONTENT==========

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sergio Rivera} \\ \vspace{1pt}
    \href{mailto:sr2070@cantab.ac.uk}{\underline{sr2070@cantab.ac.uk}} $|$ 
    \href{https://linkedin.com/in/sergioriveralopez}{\underline{linkedin.com/in/sergioriveralopez}} $|$
    \href{https://github.com/sergiorivera50}{\underline{github.com/sergiorivera50}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cambridge}{Cambridge, UK}
      {MPhil in Advanced Computer Science (80.67/100, Distinction)}{Oct. 2023 -- Jun. 2024}
    \resumeSubheading
      {Swansea University}{Swansea, UK}
      {BSc in Computer Science (83.86/100, First Class)}{Sep. 2019 -- May 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \bcomment{
        \resumeSubheading
          {Universidad Pontificia de Comillas}{Madrid, ES}
          {Machine Learning Lecturer}{Jan. 2026 -- Apr. 2026}
          \resumeItemListStart
            \resumeItem{Teaching the Geometric Deep Learning module in the Master's in Artificial Intelligence program (5 hours/week).}
            \resumeItem{Leading course design and delivery covering Graph Neural Networks, spatial reasoning, and AI applications in geometric domains while maintaining full-time role at Deloitte.}
          \resumeItemListEnd
    }
    
    \resumeSubheading
        {Deloitte}{Madrid, ES}
        {Data Scientist}{Jun. 2024 -- Present}
        \resumeItemListStart
            \resumeItem{Led the development of one of Spain's largest ``next best offer" neural network models for a major food retailer, impacting 4.5M clients on a weekly basis, projected to generate €50M in incremental sales over the next three years}\resumeItem{Developed data-driven marketing attribution models for a global luxury goods conglomerate, delivering a drastically enhanced understanding of their sales conversion funnels}
            \resumeItem{Delivered in-person technical presentations to cross-functional client stakeholders, effectively communicating complex AI solutions to technical teams, marketing departments, operational divisions, and business executives}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
 
    \resumeSubheading
      {Cambridge Department of Computer Science}{Cambridge, UK}
      {Graduate Researcher}{Oct. 2023 -- Jun. 2024}
      \resumeItemListStart
        \resumeItem{Conducted research on using generative ML models (GAN, VAE, Diffusion) to accelerate centralized optimal control problem planners for multi-drone trajectories with \href{https://www.cst.cam.ac.uk/people/asp45}{\underline{Prof Amanda Prorok}}, scoring an 85/100 grade on my MPhil thesis at Cambridge} \resumeItemListEnd

    \resumeSubheading
      {IBM}{Hursley, UK}
      {Software Engineer}{Jun. 2021 -- Aug. 2022}
      \resumeItemListStart
        \resumeItem{Conducted NLP research on media bias detection by fine-tuning a BERT model using PyTorch to accurately identify abusive speech in news articles, scoring detection levels close to 80\% accuracy}
        \resumeItem{Implemented a high-availability infrastructure Kubernetes cluster, centralizing logging from a network of several production servers, capturing over 1.4M logs weekly, leading to a 90\% reduction in search times for critical-level messages}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Statistical Arbitrage between Highly Cointegrated ETF Pairs}}{\emph{Feb. 2025}}
          \resumeItemListStart
            \resumeItem{Backtested mean-reversion trading strategies generating long/short signals for a derived spread instrument}
            \resumeItem{Performed the Engle-Granger two-step method for cointegration to statistically validate the mean-reversion assumption, leading to the selection of 10 American ETF pairs}
            \resumeItem{Analyzed the normality of my strategy’s returns using the Shapiro-Wilk, D'Agostino-Pearson, and Jarque-Bera tests, verifying core assumptions to accurately interpret Sharpe and Calmar ratios}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Device-Friendly Privacy-Preserving Generative Adversarial Networks}}{\emph{Jan. 2024}}
          \resumeItemListStart
            \resumeItem{Developed a novel compression framework for privacy-preserving generative adversarial networks (GANs), achieving 63.6\% memory reduction and 49.8\% reduction in floating-point operations while maintaining generation quality}
            \resumeItem{Implemented model distillation, channel pruning, and weight quantization techniques using PyTorch to create resource-efficient models compatible with edge devices}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Software Engineering}{: Python, C++, SQL, Docker, Kubernetes, Git, FastAPI, BigQuery, Google Cloud, JavaScript} \\
     \textbf{AI/ML Libraries}{: PyTorch, TensorFlow, Scikit-Learn, XGBoost, NumPy, Pandas, SciPy, Matplotlib, Polars, SHAP} \\
     \textbf{Spoken Languages}{: Spanish (native), English (bilingual)} \\
    }}
 \end{itemize}
\end{document}
